Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-29 stp/paper/main.tex
Fixed results

In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
This observation provides further evidence of the validity of our new framework.  
\begin{table}[!ht]\small
  \centering 
  \vspace*{-0.6em}
  \caption{Performance with unknowns manually removed% for leave one out strategy.
  	  \vspace*{-0.8em}}
  	\label{tab:nounkn}
  	\scalebox{0.8}{
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{Precision} & 
  		\multicolumn{2}{c}{Recall}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		\karma{} &  0.72 & 0.87 & 0.54 & 0.61 \\
 		\serene{} & 0.82 & 0.86 & 0.62 & 0.75 \\
		\serenepats{} & 0.6 & 0.86 & 0.64 & 0.75 \\  		
  		\hline
		\end{tabular} 
		}
\vspace*{-2mm}
\end{table}

>>>>

In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes for the leave-one-out setting.
In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
%This observation provides further evidence of the validity of our new framework.
The first solutions found by \serenepats{} tend to be bigger than those of \serene{}: hence the precision suffers, but the recall is better.
We have further observed that given enough time \serenepats{} finds much better solutions both in precision and recall.

\begin{table}[!ht]\small
  \centering 
  \vspace*{-0.6em}
  \caption{Performance with unknowns manually removed% for leave one out strategy.
  	  \vspace*{-0.8em}}
  	\label{tab:nounkn}
  	\scalebox{0.8}{
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{Precision} & 
  		\multicolumn{2}{c}{Recall}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		\karma{} &  0.72 & 0.81 & 0.54 & 0.64 \\
 		\serene{} & 0.82 & 0.85 & 0.62 & 0.75 \\
		\serenepats{} & 0.6 & 0.86 & 0.64 & 0.75 \\  		
  		\hline
		\end{tabular} 
		}
\vspace*{-2mm}
\end{table}
